Video Understanding : A review of action detection-recognition dataset*\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-01-12 conference_101719.tex
origin

\textbf{Advancement of computer hardware} :

\begin{center}
	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
	\caption{Example of a figure caption.}
	\label{SSD300} 
\end{center}

>>>>

\textbf{Advancement of computer hardware} : In 1965, Gordon Moore, co-founder of Intel Corporation, made a prediction in his article that in the next ten years, the number of transistors would double every year. Ten years later, in 1975, he revised his prediction, stating that the number of transistors would double every two years. This statement became known as Moore's Law. Although in recent years Moore's Law is no longer accurate due to technological limitations, as the size of transistors needs to decrease while their density increases, the rate of growth has been impressive. For example, in 2007, the most advanced processors like the Intel Core 2 Duo were built on a 45-nanometer process and contained approximately 230 million transistors. However, in 2023, Apple introduced the Apple A17 Pro processor, built on a 3-nanometer process with approximately 19 billion transistors. During this period, deep convolutional neural network models also made significant advancements, from models like LeNet-5 with only around 60 thousand parameters to AlexNet and VGGNet with 60 million and 138 million parameters, respectively. Moreover, in the field of natural language processing, large language models have reached parameter counts in the tens of billions. These developments have been truly impressive. It is evident that the pace of technological development has greatly contributed to the advancement of the field of artificial intelligence, where a tremendous amount of computational power is required.

\begin{center}
	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
	\caption{Example of a figure.}
	\label{SSD300} 
\end{center}
